Mental Health Screening in CF - PSC Screening

### 2024-05-22 Emily Muther/mental_health_screening_psc.qmd
paths and sweat test tables plus distributions

```{r setup}
#| include: false
library(tidyverse)
library(gtsummary)
library(lme4)
library(GLMMadaptive)
library(plotly)
library(knitr)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/timvigers/OneDrive - The University of Colorado Denver/Vigers/CF"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}
#| warning: false
# Import
df <- read.csv("./Emily Muther/General - Muther Research Group/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv",
  check.names = F, na.strings = ""
)
# Remove duplicate rows
df <- df %>% distinct()
# Sort by ID and contact date
df$CONTACT_DATE <- lubridate::mdy(df$CONTACT_DATE)
df <- df %>% arrange(PAT_MRN_ID, CONTACT_DATE)
# Exclude those with no PSC data
df <- df %>% filter(!is.na(Score))
# Make visit number
df <- df %>%
  group_by(PAT_MRN_ID) %>%
  mutate(visit_num = row_number()) %>%
  ungroup()
```

@@

```{r table 2}
df %>%
  select(
    `Internalizing subscale`:`Externalizing subscale`, Score,
    `PSC Attention`:`PSC Totals`
  ) %>%
  tbl_summary(
    missing_text = "Missing",
    type = list(`Internalizing subscale` ~ "continuous")
  )
```

>>>>

```{r setup}
#| include: false
library(tidyverse)
library(gtsummary)
library(lme4)
library(GLMMadaptive)
library(plotly)
library(knitr)
home_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/Library/CloudStorage/OneDrive-TheUniversityofColoradoDenver/Vigers/CF",
  "Windows" = "C:/Users/Tim/OneDrive - The University of Colorado Denver/Vigers/CF",
  "Linux" = "/home/timvigers/OneDrive/Vigers/CF"
)
github_dir <- switch(Sys.info()["sysname"],
  "Darwin" = "/Users/timvigers/GitHub",
  "Windows" = "C:/Users/Tim/GitHub",
  "Linux" = "/home/timvigers/GitHub"
)
knitr::opts_knit$set(root.dir = home_dir)
```

```{r data cleaning}
#| warning: false
# Import
df <- read.csv("./Emily Muther/General/Mental Health Screening/Data_Raw/PSC_Full_Data_data_11-11-22.csv",
  check.names = F, na.strings = ""
)
# Remove duplicate rows
df <- df %>% distinct()
# Sort by ID and contact date
df$CONTACT_DATE <- lubridate::mdy(df$CONTACT_DATE)
df <- df %>% arrange(PAT_MRN_ID, CONTACT_DATE)
# Exclude those with no PSC data
df <- df %>% filter(!is.na(Score))
# Make visit number
df <- df %>%
  group_by(PAT_MRN_ID) %>%
  mutate(visit_num = row_number()) %>%
  ungroup()
```

@@

```{r table 2}
df %>%
  select(
    `Internalizing subscale`:`Externalizing subscale`, Score,
    `PSC Attention`:`PSC Totals`
  ) %>%
  tbl_summary(
    missing_text = "Missing",
    type = list(`Internalizing subscale` ~ "continuous")
  )

ggplot(df,aes(x=Score))+
  geom_histogram(binwidth = 1) +
  theme_bw()
```
